### 2023-04-03 manuscript.tex
Improve explanation
The MSO definition of transitive closure assumes that relations are
nonrecursive, otherwise a FO definition can as well be given.
Moreover, it uses transitive sets with respect to a relation.

* manuscript.tex:

Alternatively, regular relations can be represented as logical
transductions, specifically \textterm{monadic second-order} ones as
those of \textcite{eh01mdsttft}, which are actually able to represent
nonregular relations.\footnote{An example is the first-order definable
  total reduplication \(w \to ww\), whose output language is included
  in the class of tree-adjoining languages \parencite{sw94efecg}.}
Monadic second-order logic allows quantification over sets, which is
needed for the definition of general precedence \(<\) based on
immediate precedence \(\vartriangleleft\):

\ex.
\a. \(\mathit{Closed}(X) \coloneq \forall x, y\ldotp
(x \in X \land x \vartriangleleft y) \implies y \in X\)
\b. \(x < y \coloneq \forall X\ldotp
(x \in X \land \mathit{Closed}(X)) \implies y \in X\)

This is understood as \enquote{\(x\) precedes \(y\) iff every
  transitive closure of immediate precedence that includes \(x\) also
  includes \(y\)}, which means the minimal one of such transitive
closures also includes \(y\).  A relation is then defined that
expresses that an \(a\) immediately precedes another \(a\) ignoring
other non-\(a\)s between them:

>>>>

Alternatively, regular relations can be represented as logical
transductions, specifically \textterm{monadic second-order} ones as
those of \textcite{eh01mdsttft}, which are actually able to represent
nonregular relations.\footnote{An example is the first-order definable
  total reduplication \(w \to ww\), whose output language is included
  in the class of tree-adjoining languages \parencite{sw94efecg}.}
Monadic second-order logic allows quantification over sets, which is
needed for the definition of general precedence \(<\) based on
immediate precedence \(\vartriangleleft\):\footnote{This is to assume
  the relations are nonrecursive.}

\ex.
\a. \(\mathit{Transitive}(X) \coloneq \forall x, y\ldotp
(x \in X \land x \vartriangleleft y) \implies y \in X\)
\b. \(x < y \coloneq \forall X\ldotp
(x \in X \land \mathit{Transitive}(X)) \implies y \in X\)

This is understood as \enquote{\(x\) precedes \(y\) iff every
  transitive set with respect to immediate precedence that includes
  \(x\) also includes \(y\)}, which means the transitive closure also
includes \(y\).  A relation is then defined that expresses that an
\(a\) immediately precedes another \(a\) ignoring other non-\(a\)s
between them:
